\cvsection{Education}
\smallskip
\cvevent{Bachelor of Engineering - 9.71/10 CGPA }{Savitribai Phule Pune University}{ June 2018 - June 2022}{}
% \cvevent{Higher Secondary - 80\%}{State Board of Secondary Education}{ 2018 }{}
% \cvevent{Secondary - 91\%}{State Board of Secondary Education}{ 2016 }{}


\cvsection{Projects}
\smallskip
\cvproject{QuickNote - Note taking WebApp : \href{https://github.com/MasterZesty/QuickNote}{\textcolor{blue}{\underline{\textnormal{Github}}}}}
\smallskip
\begin{itemize}
\item Developed full-stack Django web app with user authentication, enabling registration, login, and personalized note management.
\smallskip
\item Created intuitive and responsive interface for effortless note creation, viewing, editing, and deletion, elevating user experience.
\end{itemize}
\smallskip
\smallskip
\cvproject{QuizTaker - Quiz WebApp : \href{https://github.com/MasterZesty/QuizTaker}{\textcolor{blue}{\underline{\textnormal{Github}}}}}
\smallskip
\begin{itemize}
\item Developed a full-stack Django application enabling users to create multiple-choice quizzes, allowing participants to engage in quizzes while showing results dynamically on a centralized leaderboard.
\smallskip
\item Used Django, Python, HTML, Tailwind CSS, JavaScript, MySQL.
\end{itemize}
\smallskip
\smallskip
\cvproject{Log Ingestor With Query Interface : \href{https://github.com/MasterZesty/log-ingestor-with-query-interface}{\textcolor{blue}{\underline{\textnormal{Github}}}}}
\smallskip
\begin{itemize}
\item Developed a scalable Log Ingestor and Query Interface using Python, Kafka, Flask, and MySQL. Manages extensive log data efficiently, enabling simplified querying through selectable attribute filters.
\smallskip
\item The Log Ingestor, developed in Python using Flask, includes a Log Publisher Service with an API endpoint that receives and parses JSON log data, pushing it to a Kafka topic.
\smallskip
\item  Another service, Log Consumer, subscribes to Kafka topic, storing logs in the primary database through Flask in Python.
\smallskip
\item The Query Interface features an intuitive user interface developed with HTML, Tailwind CSS and JavaScript. It allows users to select specific attributes for querying, streamlining log data retrieval.
\end{itemize}
\cvproject{}

\cvsection{Extracurricular}
\smallskip
\begin{itemize}
\item Team lead for e-yantra innovation challenge project competition 2020-21.
\smallskip
\item Team Lead of team red baron PCCOE motorsports club 2020-22.
\end{itemize}